The effects of priming in human computation

### 2014-05-08 docs/draft/figs.tex
add treatments table

\begin{document}
\begin{figure}
	\includegraphics{figs/f1-thetas.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa. }
\end{figure}

>>>>

\begin{document}
\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder$^a$ & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

%\begin{addmargin}[11em]{11em}
%	\vspace{2mm}
%	$^a$\footnotesize{The full funder names used were ``The Glodal Foundation
%		for Cultural Recognition'' and ``The National Foundation for 
%		Nutritional Awareness''.}
%\end{addmargin}

	\caption{Experimental treatments.  Workers were uniformly randomly
		assigned to one of the treatments listed above.  The full funder 
		names used were ``The Glodal Foundation
		for Cultural Recognition'' and ``The National Foundation for 
		Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
		priming images used are shown in \textbf{Figs. B}, \textbf{C}, and 
		\textbf{D}.}
	\label{table:1}
\end{table}

\begin{figure}
	\includegraphics{figs/f1-thetas.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa. }
\end{figure}

### 2014-05-08 docs/draft/pnas1.tex
add treatments table

\usepackage{framed, color}
\usepackage{soul}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

@@

We test hysteresis by presenting AMT workers with
five images that depict meals with strong cultural overtones, and ask them to
label each image with descriptive words.  Before presenting test images,
we expose the workers to different priming treatments.  We observe how priming
treatments effect the workers' subsequent choice of labels, by looking at 
how specific the labels are, and how often workers make 
cultural references.

We employ two priming modalities in this study.  
In the first modality, which we call \textit{in-task priming}, workers are 
shown one of three sets of priming images.  The \textit{cultural}
image set, \textbf{Fig. 2}, shows images chosen for their clear depiction of an
iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. 3}, 
shows separated food ingredients, as opposed to the prepared meals shown in 
the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
image set contains images of prepared meals, and is most similar to the test 
set, but there are no prominent traces of cultural reference.  These images 
are shown right
before the test images, and they must be labeled in the same way.  From the 
workers' view-point there is no distinction between the priming and test 
images.

@@

@@

But the the underlying mechanisms in priming
can be exceedingly subtle \cite{BJOP:BJOP1796}.  As one expects exposing 
participants to an image hels them subsequently recognise that 
image when seen in a tachistoscope.  The researches demonstrated that priming 
using an image that was visually different but of an object having the same 
name also helped participants subsequently identify the image in the 
tachistoscope.  But surprisingly, being presented with related word and 
reading it aloud did not help.  On the basis of these 
results, the researchers suggest the existence of a visual-semantic system,
distinct from the linguistic one \cite{BJOP:BJOP1796}.

@@

\section*{Figure Legends}
\paragraph{Figure 1.}
$F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa.

>>>>

\usepackage{framed, color}
\usepackage{soul}
\usepackage[colorlinks=false, urlcolor=blue]{hyperref}

@@

We test hysteresis by presenting AMT workers with
five images that depict meals with strong cultural overtones 
(see \textbf{Fig. A}), and ask them to
label each image with descriptive words.  Before presenting test images,
we expose the workers to different priming treatments.  We observe how priming
treatments effect the workers' subsequent choice of labels, by looking at 
how specific the labels are, and how often workers make 
cultural references.

We employ two priming modalities in this study.  
In the first modality, which we call \textit{in-task priming}, workers are 
shown one of three sets of priming images.  The \textit{cultural}
image set, \textbf{Fig. B}, shows images chosen for their clear depiction of an
iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. C}, 
shows separated food ingredients, as opposed to the prepared meals shown in 
the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
image set contains images of prepared meals (\textbf{Fig D}), and is most 
similar to the test set, but there are no prominent traces of cultural 
reference.  These images are shown right
before the test images, and they must be labeled in the same way.  From the 
workers' view-point there is no distinction between the priming and test 
images.

@@

We also test interaction effects between framing and in-task priming.  The
various treatments are listed in \textbf{Table 1}.

@@

But the the underlying mechanisms in priming
can be exceedingly subtle \cite{BJOP:BJOP1796}.  As one expects exposing 
participants to an image hels them subsequently recognise that 
image when seen in a tachistoscope.  The researches demonstrated that priming 
using an image that was visually different but of an object having the same 
name also helped participants subsequently identify the image in the 
tachistoscope.  Surprisingly, being presented with related word and 
reading it aloud did not help.  On the basis of these 
results, the researchers suggest the existence of a visual-semantic system,
distinct from the linguistic one \cite{BJOP:BJOP1796}.

@@

\section*{Figure Legends}

\paragraph{Table 1.}
	Experimental treatments.  Workers were uniformly randomly
	assigned to one of the treatments listed above.  The full funder 
	names used were ``The Glodal Foundation
	for Cultural Recognition'' and ``The National Foundation for 
	Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
	priming images used are shown in \textbf{Figs. B}, \textbf{C}, and 
	\textbf{D}.

\paragraph{Figure A.}
	Testing image set. These images were presented to all workers in the order 
	shown after the priming set of images.

\paragraph{Figure B.}
	Ambiguous image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.

\paragraph{Figure C.}
	Cultural image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.

\paragraph{Figure D.}
	Ingredients image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.

\paragraph{Figure 1.}
$F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa.
